Comparison of Global Solution Methods to a Zero Lower Bound Model

### 2019-04-20 Paper/Paper.tex
Finish and turn in paper

\title{Comparison of Global Solution Methods to a Zero Lower Bound Model}
\date{\small First Draft: \today}
\author{Emily Martell\thanks{Thank you to Professor Throckmorton for advising and providing materials for this project. Thank you to Professor Campbell, Professor Han, Professor Rolek, and Professor Throckmorton for serving on my committee.}}
\begin{document}
\maketitle
\bigskip
\begin{center}
\fontsize{14pt}{\baselineskip}\sc Abstract%\normalfont
\end{center}

@@

{\small \forceindent During the Great Recession, the U.S. Federal Reserve lowered policy rates to zero, creating a kink in its policy rule, and calling into question traditional solution methods. Recent work has explored fully nonlinear models to represent the ZLB, but not much work has compared the performance of different solution methods. Two suggested solution methods are linear interpolation This paper examines the effect of making the policy functions conditional on whether the ZLB binds. We consider a fully nonlinear New Keynesian model with capital, and a solution algorithm with policy function iteration and linear interpolation. We find no evidence that the regime-indexed policy functions are smoother. In addition, the solution algorithms perform similarly with respect to accuracy, but the solution containing the regime-indexed policy functions is much slower, all else equal.}
\end{changemargin}
\vfill
\pagebreak

@@

As a result of the global financial crisis of 2007-9 and the subsequent recession, central banks lowered
their policy rate to its zero lower bound (ZLB). Although the ZLB constraint has always existed,
for most of the data prior to the recession, policy rates were well above zero. In the wake of this
unprecedented lowering of policy rates, the ZLB holds for a considerable portion of historic data
for three major economies --- the US, Japan, and the Euro Area. The ZLB creates a kink in the policy
rule and calls into question linear estimation methods.

@@

The \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} solution method is policy function iteration with linear interpolation to approximate future variables.  The state space features evenly-spaced nodes and exogenous state variables  approximated with the Markov chain from \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}}. The Rouwenhorst approximation is useful because it only requires interpolation along the dimensions of the endogenous state variables. This yields a faster and more accurate solution than quadrature methods.They update the policy functions with linear interpolation to accurately capture the kink experienced at the ZLB.

The \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution method approximates policy functions underlying the model's decision rule using an antistropic Smolyak method with Chebyshev polynomials. (See \hyperlink{Judd2}{\color{black}{Judd et al.\ (2014)}} for a discussion of antistropic Smolyak methods). They approximate the exogenous state variables using Gauss-Hermite quadrature. Instead of directly computing the policy functions, they estimate functions at and away from the ZLB, which builds on \hyperlink{Christiano}{\color{black}{Christiano and Fisher (2000)}}. The idea is that the policy functions feature a kink or non-differentiability at the ZLB and regime-indexing the policy functions will yield smoother functions.

@@

%In a NK model instead???
The standard representation of the Euler equation is
\begin{gather*}
u'(c_t)  = \beta u'(c_{t+1})[f'(k_{t+1}) + 1 - \delta],
\end{gather*}
where $u(\cdot)$ is the instantaneuous utility function, $0<\beta<1$ is the discount factor, $c_t$ is consumption at period $t$, $k_t$ is the capital stock at the beginning of the period, $0 < \delta \leq 1$ is the rate of depreciation, and $f(\cdot)$ is the production function. $u(\cdot)$ and $f(\cdot)$ are differentated according to the choice variables. The Euler equation is the fundamental dynamic equation in intertemporal optimization problems that include dynamic constraints. It states that the marginal cost of forgoing consumption today must equal the discounted marginal benefit of investing in capital for one period.   %Cite Dr Richter's notes?

%Here make a better segway
The interest rate appears in the household's budget constraint in models where the household has the choice of owning a nomimal bond. The household must choose a combination of consumption, labor, and bond holdings to maximize expected lifetime utility. Thus, the household's choice of consumption depends on the interest rate and whether the economy is at the ZLB. To approximate regime-indexed consumption policy functions $c_t^{ZLB}$ and $c_t^{normal}$, we provide initial guesses based on the log-linear solution. We refine the policy function guesses as follows: For each node in the state space, we solve for the time $t$ variables with either the $c_t^{ZLB}$  or $c_t^{normal}$ according to $i_t$, the interest rate at time $t$. With the time $t$ variables, we linearly interpolate both policy functions. Next, we calculate the interest rate on each node in the state space, construct an aggregate consumption policy function based on whether the economy is at the ZLB on each node, and calculate time $t+1$ variables acordingly. We then update $c_t^{ZLB}$ with an interest rate of 1, and $c_t^{normal}$ with $i_t$.

@@

In terms of accuracy, both the ART and GHLS yield similar Euler equation errors, with ART being slightly more accurate for the model with capital. The ART method converges much more quickly than the GHLS method, particularly when capital is introduced to the model. There is not a clear advantage of the regime-indexed policy function approximation when using an evenly spaced grid with linear interpolation. All else equal, using regime-indexed policy functions increases the computing time. However, introducing Chebyshev polynomials and sparse grid methods as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} may reduce solution time and allow us to solve larger models with more state variables. Further research could explore how much accuracy is gained or lost relative to using non regime-indexed policy functions approximated with Chebyshev polynomials.

@@

\section[Section 2]{Model \hypertarget{Section 2}{}} 
This is a widely-employed New Keynesian model which is similar to the model in \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, but includes capital accumulation as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}}. Thus, it is an appropriate model to benchmark the accuracy and speed of the two solution methods.

@@

\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the model parameters. Parameters are from \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, and are chosen to be characteristic of U.S. data. The subjective discount factor, $\beta$ is set to $0.9949$, the time average of the values implied by the steady-state consumption Euler equation and the federal funds rate. The Frisch labor supply elasticity $1/\eta$ is set to 3 to match the macro estimate in \hyperlink{Peterman}{\color{black}{Peterman (2016)}}. The price elasticity of substitution $\theta$ is set to 6, matching GHLS and corresponding to to a 20\% average markup. Steady-state labor hours $\bar{n}$ is set to 1/3 of available time. The steady-state risk premium, growth rate, and inflation rate are set to the time averages of per capital real DGP growth, the percent GDP implicit price deflator, and the Baa corporate bond yield relative to the yield on the 10-Year Treasury. The capital share of income $\alpha$ is equal to the \hyperlink{Fernald}{\color{black}{Fernald (2012)}} utilization-adjusted quarterly-TFP estimates of the capital share of income from 1988-2017Q4. The other parameters are set to values consistent with posterior estimates from similar models in the literature. For the model without capital, all parameters are the same except $\sigma_i$ which is set to $0.002$. (For the model with capital, $\sigma_i$ was originally set to $0.002$ to match \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, but the model failed to hit the ZLB during simulation, so we increased the parameter to $0.0035$.)

\section[Section 3]{Solution Methods \hypertarget{Section 3}{}} 
\subsection{Regime-indexed policy functions} Instead of directly approximating the policy functions, some papers elect to approximate alternative functions to avoid the kink experienced at the ZLB (e.g., \hyperlink{Gust}{\color{black}{Gust et al.,\ 2017}}; \hyperlink{Aruoba}{\color{black}{Aruoba et al.,\ 2018}}). \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} uses policy functions that are indexed by the interest-rate regime. Because these functions do not depend on the current indicator function,\hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} claims that they are more likely to be smooth. The regime-specific functions still depend on a secondary effect that the non-differentiability in the nominal rate in the following period has on expectations of future variables.  However, following \hyperlink{Christiano}{\color{black}{Christiano and Fisher (2000)}} this effect should be small due to the presence of the expectations operators which act to smooth out regime-specific functions. The idea for regime-indexed policy functions is as follows:
\begin{gather}
    \label{eq:18}
  \textbf{pf}_t(d) = \textbf{pf}_{t,1}(d)\mathds{I}_t(d) + \textbf{pf}_{t,2}(d)(1-\mathds{I}_t(d)),
\end{gather}

where $\mathds{I}_t(d)$ is defined by
\begin{gather}
    \label{eq:19}
  \mathds{I}_t(d) = 
\begin{cases}
     1 &\text{ if } i_t > 1\\
     0 &\text{ otherwise.}
\end{cases}
\end{gather}
The variable $i_t=\max\{1,i_t^n\}$ represents the value of the notional rate derived from evaluating the functions $\textbf{pf}_{t,j}(d)$ for $j \in \{1,2\}$ and using equation (\ref{eq:16}). (For each variable, $j=1$ denotes the function associated with the regime with a positive nominal rate and $j=2$ denotes the function associated with the ZLB regime.) %In calculating the fixed point, we use $i=1$ when the model is in the ZLB regime. 
The functions $\textbf{pf}_{t,j}$ satisfy the residual functions $R_{t,l,j}$ for and $l \in \{1,2,3,4\}$ which correspond to the household FOC bond, FOC capital, FOC investment, and the price Phillips curve, respectively, and $j = 1,2$.
\begin{gather}
\label{eq:20}
  R_{t,1,1} = 1 - s_ti_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))],\\
\label{eq:21}
  R_{t,1,2} = 1 - s_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))],\\
\label{eq:22}
  R_{t,2,j} = q_t - \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})],\\
\label{eq:23}
  R_{t,3,j} = 1 - q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] - \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)],\\
\label{eq:24}
  R_{t,4,j} = \varphi(\pi_t^{gap}-1)\pi_t^{gap} - (1-\theta) - \theta mc_t - \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)].
  \end{gather}

\subsection{Solution Algorithm}
Our solution algorithm is as follows: Construct an evenly-spaced grid by discretizing the endogenous state variables and using \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}} method to approximate the exogenous processes for $s_t$, $g_t$, and $\varepsilon_{i,t}$. We use the Rouwenhorst method so that we do not have to interpolate along the dimensions of the exogenous state variables, providing a faster and more accurate than quadrature methods. The vector of policy functions is denoted $\textbf{pf}_t$ and the realization on node $d$ is denoted $\textbf{pf}_t(d)$. Denote the vector of states $\textbf{z}_t$. 
\begin{enumerate} 
\item To construct the initial policy functions $\textbf{pf}_0$, we solve the log-linear analog of our model with the ZLB not impos
ed using \hyperlink{Sims}{\color{black}{Sims's (2002) \texttt{gensys}}} algorithm. (For GHLS, we initialize the regime-indexed policy functions by setting them to the log-linear solution.)
\item For each node in the state space $d \in \{1,\dots,D\}:$
\begin{enumerate}
\item Solve for the variables dated at time $t$ given $\textbf{pf}_t$ and $\textbf{z}_t$. (For GHLS, we calculate time $t$ variables with the non-ZLB policy functions if the interest rate $i_t > 1$, and the ZLB policy functions if the interest rate $i_t \leq 1$). 
\item  Linearly interpolate the policy functions at the updated state variables $\textbf{z}_{t+1}$ to obtain $\textbf{pf}_{t+1}(m)$ on every integration node $m \in \{1,\dots,M\}$. (For GHLS, we interpolate the non-ZLB and ZLB policy functions separately.)
\item Given the interpolated policy functions $\{\textbf{pf}(m)\}_{m=1}^M$, and integration nodes and weights provided by the Rouwenhorst method, approximate the expectation operators for the model. (For GHLS, use the interest rate array calculated from the interpolated policy functions to determine whether the model is at the ZLB at each node. We construct the aggregate policy functions accordingly, as in (\ref{eq:18}) and (\ref{eq:19}).)
\item Solve for time $t+1$ variables from the expectation operators. Back out the policy functions $\textbf{pf}_{d}$ from the expectation operators and time $t+1$ variables. (For GHLS, we solve for the regime-indexed policy functions according to (\ref{eq:20})-(\ref{eq:24})).
\end{enumerate}
\item Repeat step 2 until the maximum distance between successive approximations of the policy functions is below $10^{-6}$. 
\end{enumerate}

  \subsection{Euler Equation Errors}
We use Euler equation errors to measure the accuracy of our solutions. To measure errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method following ART to allow exogenous variables to have realizations between grid points. The Euler equation errors are represented in absolute value of the errors in base 10 logarithms. An Euler equation error of -3 means the household makes an error equivalent to one per 1,000 consumption goods; i.e., an error of 0.1\% on average.

@@

\begin{table}[H]
  \centering
\captionsetup{justification=centering}
  \hypertarget{Table 2}
  \small
    \setlength{\tabcolsep}{6pt}      
  \begin{tabular}{l c c c c c c}
    \hline
    & \multicolumn{3}{c}{Model without capital} & \multicolumn{3}{c}{Model with capital} \\
    & Total nodes & Iterations & Total Time & Total Nodes & Iterations & Total time\\
    \hline
  ART & 2401  & 67 & 17.9s & 78125 & 65 & 0h 15m 37.1s\\    
  GHLS & 2401  & 66 & 46s & 78125 & 1170 &  5h 32m 48.6s\\
  \hline
\end{tabular}
  \caption{Solution times}
\end{table}

@@

The GHLS method is slower for both the model with and without capital. The speed
differential blows up for the model with capital. The performance is somewhat contingent upon the
parameterization. The GHLS method was faster with $\sigma_v = 0.002$, but we selected $\sigma_v = 0.0035$
so that the ZLB constraint was better represented in the simulation. The GHLS solution
algorithm handles a labor policy (consumption policy for model without capital) at and away from
the ZLB. As a result, the solution algorithm requires two interpolation steps. In addition, the GHLS solution algorithm must determine at which nodes the state space is at the ZLB, and
solve for time $t$ and $t + 1$ variables accordingly.

@@

\subsection{Policy Functions} \hyperlink{Figure 1}{Figure 1} shows the cross-section of the labor policy functions with the interest rate and risk premium for the model with capital. The black dots on the nodes of the
graph represent labor values corresponding to the ZLB. The GHLS labor policy function is
computed at and away from the ZLB, and combined later, so all three are shown in the figure. The
GHLS combined policy function is very similar to the policy function away from the ZLB.

Visually, the ART labor policy function is smoother. Labor hours smoothly
increase as the interest rate falls and hits the ZLB. The GHLS labor policy function
features a kink at the ZLB where labor rises dramatically.

\begin{table}[H]
  \centering
\captionsetup{justification=centering}
  \hypertarget{Table 3}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Mean \% Error & RMSE & Mean \% Error & RMSE\\
    \hline
    ART policy & 0.46545\% &0.0020137 $c$  units & 0.19585\% & .0029035 $l$ units \\    
  GHLS policy & 0.45556\% & 0.0019792 $c$ units & 0.56142\% & 0.0076665 $l$ units \\
  \hline
\end{tabular}
  \caption{Smoothness measures for labor policy functions ($c$ for model with capital and $n$ for model with capital). GHLS combined policy functions are reported.}
\end{table}

 \hyperlink{Table 3}{Table 3} reports the RMSE (root mean square error) and mean percent error from linear policy
functions. The mean percent error is calculated as $1/M\sum_{i=1}^N[\textbf{pf.n}(i)-\hat{\textbf{n}}(i)]/\bar{n}$
where $N$ is the
number of periods, $\textbf{pf.n}$ is the labor policy function, $\hat{\textbf{n}}$ is the linear regression model of $\textbf{pf.n}$ fit to
the state variables, and $\bar{n}$ is steady state labor. The corresponding results for the model without
capital is reported in \hyperlink{Appendix C}{Appendix C}.

The RMSE and the mean percent error indicate that the ART labor policy function is smoother and better fits a linear plane for the model with capital. For the model without
capital, both functions are smooth, but the GHLS policy function slightly better fits a linear
plane than the ART policy function.

\begin{figure}[H]
\hypertarget{Figure 2}  
    \centering
\captionsetup{justification=centering}
    \includegraphics[width=16cm,scale=.8]{eeerrorsCAP.pdf}%{pfs3D_CAPITAL.eps}
  \caption{Euler equation errors for model with capital}    
  \end{figure}

\subsection{Euler Equation Errors} \hyperlink{Figure 2}{Figure 2} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the household FOC bond, FOC capital, FOC investment, and price Phillips curve in the model with capital. We also report the mean and maximum error. The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.

The Euler equation errors are very similar between solution algorithm, though the ART
Euler equation errors are slightly more negative, and thus correspond to a smaller household error.
The mean errors are similar, though the maximum error is considerably higher for the GHLS
Euler equation error. The shapes of the errors are comparable.

>>>>

\title{Comparison of Global Solution Methods to a Zero Lower Bound Model}
\date{\small\today}
\author{Emily Martell\thanks{Thank you to Professor Throckmorton for advising and providing materials for this project. Thank you to Professor Campbell, Professor Han, Professor Rolek, and Professor Throckmorton for serving on my committee.}}
\begin{document}
\maketitle
\bigskip
\begin{center}
\fontsize{14pt}{\baselineskip}\sc Abstract%\normalfont
\end{center}

@@

{\small \forceindent During the Great Recession, the U.S. Federal Reserve lowered policy rates to zero, introducing a kink in its policy rule and calling into question traditional solution methods. Recent papers have solved fully nonlinear models that treats the zero lower bound (ZLB) as an occasionally binding constraint, but there is little work analyzing the relative performance of these nonlinear solution methods. Two proposed solution methods are policy function iteration with linear interpolation and regime-indexed policy function iteration with Chebyshev polynomial approximation. We examine the impact of making the policy functions conditional on whether the ZLB binds. Our solution algorithm uses evenly-spaced grid points, linear interpolation, and Rouwenhorst integration. This paper shows that the regime-indexed policy functions are quite nonlinear in a New Keynesian model with capital and are costly to approximate in terms of solution time.}

\end{changemargin}
\vfill
\pagebreak

@@

As a result of the global financial crisis of 2007-9 and the subsequent recession, central banks lowered
their policy rate to its zero lower bound (ZLB). Although the ZLB constraint has always existed,
for most of the data prior to the recession, policy rates were well above zero. In the wake of this
unprecedented lowering of policy rates, the ZLB holds for a considerable portion of historic data
for three major economies --- the US, Japan, and the Euro Area. The ZLB introduces a kink in the policy
rule and calls into question linear estimation methods.

@@

The \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} solution method is policy function iteration with linear interpolation to approximate future variables.  The state space features evenly-spaced nodes and exogenous state variables  approximated with the Markov chain from \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}}, which \hyperlink{Kopecky}{\color{black}{Kopecky and Suen (2010)}} show outperforms other methods for approximating autoregressive processes. The Rouwenhorst approximation is useful because it only requires interpolation along the dimensions of the endogenous state variables. They update the policy functions with linear interpolation to accurately capture the kink experienced at the ZLB.

The \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution method approximates policy functions underlying the model's decision rule using an antistropic Smolyak method with Chebyshev polynomials. (See \hyperlink{Judd2}{\color{black}{Judd et al.\, 2014}} for a discussion of antistropic Smolyak methods). They approximate the exogenous state variables using Gauss-Hermite quadrature. Instead of directly computing the policy functions, they estimate functions at and away from the ZLB, which builds on \hyperlink{Christiano}{\color{black}{Christiano and Fisher (2000)}}. The idea is that the policy functions feature a kink or non-differentiability at the ZLB and regime-indexing the policy functions will yield smoother functions. This is appropriate for the choice of Chebyshev polynomial approximation, which performs better on smoother functions.

@@

%In a NK model instead???
The interest rate enters directly in the consumption Euler equation, which for our small-scale model without habit formation is as follows:
\begin{gather*}
    1 = \beta E_t[(c_t/c_{t+1})(s_ti_t/\pi_{t})],
\end{gather*}
where $E_t$ is the expectation operator, $0<\beta<1$ is the discount factor, and $c_t$, $s_t$, $i_t$, and $\pi_t$ are consumption, the risk premium, the interest rate, and inflation at time $t$. The interest rate appears because the household has the choice of owning a nominal bond, and must choose a combination of consumption, labor, and bond holdings to maximize expected lifetime utility. For this reason, consumption $c_t$ depends on the interest rate. At the ZLB, the presence of the interest rate creates a nonlinearity in the consumption Euler equation and motivates the use of regime-indexed policy functions.

To approximate regime-indexed consumption policy functions $c_t^{ZLB}$ and $c_t^{normal}$, we provide initial guesses based on the log-linear solution. We refine the policy function guesses as follows: For each node in the state space, we solve for the time $t$ variables with either $c_t^{ZLB}$  or $c_t^{normal}$ according to $i_t$, the interest rate at time $t$. With the time $t$ variables, we linearly interpolate both policy functions. Next, we calculate the interest rate on each node in the state space, construct an aggregate consumption policy function based on whether the economy is at the ZLB on each node, and calculate time $t+1$ variables accordingly. We then update $c_t^{ZLB}$ with an interest rate of 1, and $c_t^{normal}$ with $i_t$.

@@

In terms of accuracy, both ART and GHLS yield similar Euler equation errors, with ART being slightly more accurate for the model with capital. The ART method converges much more quickly than the GHLS method, particularly when capital is introduced to the model. There is not a clear advantage of the regime-indexed policy function approximation when using an evenly spaced grid with linear interpolation. All else equal, using regime-indexed policy functions increases the computing time. However, introducing Chebyshev polynomials and sparse grid methods as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} may reduce solution time and allow us to solve larger models with more state variables. Further research could explore how much accuracy is gained or lost relative to using non regime-indexed policy functions approximated with Chebyshev polynomials.

@@

\section[Section 2]{Model \hypertarget{Section 2}{}} 
Our model is a widely-employed New Keynesian model which is similar to the model in \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, but includes capital accumulation as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}}. Thus, it is an appropriate model to benchmark the accuracy and speed of the two solution methods.

@@

\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the model parameters. Parameters are from \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, and are chosen to be characteristic of U.S. data. The subjective discount factor, $\beta$ is set to $0.9949$, the time average of the values implied by the steady-state consumption Euler equation and the federal funds rate. The Frisch labor supply elasticity $1/\eta$ is set to 3 to match the macro estimate in \hyperlink{Peterman}{\color{black}{Peterman (2016)}}. The price elasticity of substitution $\theta$ is set to 6, matching GHLS and corresponding to to a 20\% average markup. Steady-state labor hours $\bar{n}$ is set to 1/3 of available time. The steady-state risk premium, growth rate, and inflation rate are set to the time averages of per capital real DGP growth, the percent GDP implicit price deflator, and the Baa corporate bond yield relative to the yield on the 10-Year Treasury. The capital share of income $\alpha$ is equal to the \hyperlink{Fernald}{\color{black}{Fernald (2012)}} utilization-adjusted quarterly-TFP estimates of the capital share of income from 1988-2017Q4. The other parameters are set to values consistent with posterior estimates from similar models in the literature. For the model without capital, all parameters are equivalent to those above except we set $\sigma_s=0.006$ and $\sigma_i=0.002$ allow the GHLS algorithm to converge.

\section[Section 3]{Solution Methods \hypertarget{Section 3}{}} 
\subsection{Regime-indexed policy functions} Instead of directly approximating the policy functions, some papers elect to approximate alternative functions to avoid the kink experienced at the ZLB (e.g., \hyperlink{Gust}{\color{black}{Gust et al.,\ 2017}}; \hyperlink{Aruoba}{\color{black}{Aruoba et al.,\ 2018}}). \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} uses policy functions that are indexed by the interest-rate regime. Because these functions do not depend on the current indicator function, \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} claims that they are more likely to be smooth. The regime-specific functions still depend on a secondary effect that the non-differentiability in the nominal rate in the following period has on expectations of future variables.  However, following \hyperlink{Christiano}{\color{black}{Christiano and Fisher (2000)}} this effect should be small due to the presence of the expectations operators which act to smooth out regime-specific functions. Let the vector of policy functions at time $t$ be denoted $\textbf{pf}_t$ and the realization on node $d$ be denoted $\textbf{pf}_t(d)$. The idea for regime-indexed policy functions is as follows:
\begin{gather}
    \label{eq:18}
  \textbf{pf}_t(d) = \textbf{pf}_{t,1}(d)\mathds{I}_t(d) + \textbf{pf}_{t,2}(d)(1-\mathds{I}_t(d)),
\end{gather}

where $\mathds{I}_t(d)$ is defined by
\begin{gather}
    \label{eq:19}
  \mathds{I}_t(d) = 
\begin{cases}
     1 &\text{ if } i_t > 1\\
     0 &\text{ otherwise.}
\end{cases}
\end{gather}
The variable $i_t=\max\{1,i_t^n\}$ represents the value of the notional rate derived from evaluating the functions $\textbf{pf}_{t,j}(d)$ for $j \in \{1,2\}$ and using equation (\ref{eq:16}). (For each variable, $j=1$ denotes the function associated with the regime with a positive nominal rate and $j=2$ denotes the function associated with the ZLB regime.) %In calculating the fixed point, we use $i=1$ when the model is in the ZLB regime. 
The functions $\textbf{pf}_{t,j}$ satisfy the residual functions $R_{t,l,j}$ for and $l \in \{1,2,3,4\}$ which correspond to the household FOC bond, FOC capital, FOC investment, and the price Phillips curve, respectively, and $j \in \{1,2\}$.
\begin{gather}
\label{eq:20}
  R_{t,1,1} = 1 - s_ti_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))],\\
\label{eq:21}
  R_{t,1,2} = 1 - s_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))],\\
\label{eq:22}
R_{t,2,j} = q_t - \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})],\\
 \label{eq:23} 
  \begin{split}
    R_{t,3,j} &= 1 - q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] \\&- \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)], 
  \end{split}
  \\
   \label{eq:24}
  \begin{split}
    R_{t,4,j} &= \varphi(\pi_t^{gap}-1)\pi_t^{gap} - (1-\theta) - \theta mc_t \\&- \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)].
    \end{split}
  \end{gather}

\subsection{Solution Algorithm}
Our solution algorithm is as follows: Construct an evenly-spaced grid by discretizing the endogenous state variables and using \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}} method to approximate the exogenous processes for $s_t$, $g_t$, and $\varepsilon_{i,t}$. We use the Rouwenhorst method so that we do not have to interpolate along the dimensions of the exogenous state variables, which is faster and more accurate than quadrature methods.  As above, the vector of policy functions is denoted $\textbf{pf}_t$ and the realization on node $d$ is denoted $\textbf{pf}_t(d)$. Denote the vector of states $\textbf{z}_t$. 
\begin{enumerate} 
\item To construct the initial policy functions $\textbf{pf}_0$, we solve the log-linear analog of our model with the ZLB not imposed using \hyperlink{Sims}{\color{black}{Sims's (2002) \texttt{gensys}}} algorithm. (For GHLS, we initialize the regime-indexed policy functions by setting them to the log-linear solution.)
\item For each node in the state space $d \in \{1,\dots,D\}:$
\begin{enumerate}
\item Solve for the variables dated at time $t$ given $\textbf{pf}_t$ and $\textbf{z}_t$. (For GHLS, we calculate time $t$ variables with the non-ZLB policy functions if the interest rate $i_t > 1$, and the ZLB policy functions if the interest rate $i_t \leq 1$). 
\item  Linearly interpolate the policy functions at the updated state variables $\textbf{z}_{t+1}$ to obtain $\textbf{pf}_{t+1}(m)$ on every integration node $m \in \{1,\dots,M\}$. (For GHLS, we interpolate the non-ZLB and ZLB policy functions separately.)
\item Given the interpolated policy functions $\{\textbf{pf}(m)\}_{m=1}^M$, and integration nodes and weights provided by the Rouwenhorst method, approximate the expectation operators for the model. (For GHLS, use the interest rate array calculated from the interpolated policy functions to determine whether the model is at the ZLB at each node. We construct the aggregate policy functions accordingly, as in (\ref{eq:18}) and (\ref{eq:19}).)
\item Solve for time $t+1$ variables from the expectation operators. Back out the policy functions $\textbf{pf}_t(d)$ from the expectation operators and time $t+1$ variables. (For GHLS, we solve for the regime-indexed policy functions according to (\ref{eq:20})-(\ref{eq:24})).
\end{enumerate}
\item Repeat step 2 until the maximum distance between successive approximations of the policy functions is below $10^{-6}$. 
\end{enumerate}

  \subsection{Euler Equation Errors}
We use Euler equation errors to measure the accuracy of our solutions. To approximate errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method following ART to allow exogenous variables to have realizations between grid points. The Euler equation errors are represented in absolute value of the errors in base 10 logarithms. An Euler equation error of -3 means the household makes an error equivalent to one per 1,000 consumption goods; i.e., an error of 0.1\% on average.

@@

\begin{table}[H]
  \centering
\captionsetup{justification=centering}
  \hypertarget{Table 2}
  \small
    \setlength{\tabcolsep}{6pt}      
  \begin{tabular}{l c c c c c c}
    \hline
    & \multicolumn{3}{c}{Model without capital} & \multicolumn{3}{c}{Model with capital} \\
    & Total nodes & Iterations & Total Time & Total Nodes & Iterations & Total time\\
    \hline
  ART & 2401  & 76 & 21.6s & 78125 & 65 & 0h 15m 37.1s\\    
  GHLS & 2401  & 62 & 18.5s & 78125 & 1170 &  5h 32m 48.6s\\
  \hline
\end{tabular}
  \caption{Solution times}
\end{table}

@@

The GHLS method is slightly faster for the model without capital, but much slower for the model with capital. The performance is somewhat contingent upon the
parameterization, but the results indicate that the speed differential blows up for the model with capital. This may be due to the following: The GHLS solution
algorithm has a labor policy (consumption policy for model without capital) both at and away from
the ZLB. As a result, the solution algorithm requires an additional interpolation step. In addition, the GHLS solution algorithm must determine at which nodes the state space is at the ZLB, and
solve for time $t$ and $t + 1$ variables accordingly.

@@

\subsection{Policy Functions} \hyperlink{Figure 1}{Figure 1} shows the cross-section of the labor policy functions with the interest rate and risk premium for the model with capital. The black dots on the nodes of the
graph represent labor values corresponding to the ZLB. The GHLS labor policy function is
computed at and away from the ZLB and combined later, and all three are shown in the figure. The
GHLS combined policy function is very similar to the policy function away from the ZLB, as only a fraction of the nodes experience the ZLB binding.

Visually, the ART labor policy function cross-section is quite a bit smoother. Labor hours smoothly
increase as the interest rate falls and hits the ZLB. The GHLS labor policy function
features a kink at the ZLB where labor rises dramatically.

For the model without capital, the GHLS policy functions do not experience as pronounced a nonlinearity.

\begin{figure}[H]
\hypertarget{Figure 2}  
    \centering
\captionsetup{justification=centering}
    \includegraphics[width=16cm,scale=.9]{pfs3D.pdf}
  \caption{Consumption policy function for model without capital}    
  \end{figure}

\hyperlink{Figure 2}{Figure 2} shows the cross-section of the consumption policy functions with the interest rate and
risk premium. The policy functions are all fairly smooth and only have a slight nonlinearity at the
ZLB. The GHLS policy functions are smoother than the ART policy function with respect to both the average percent error from a linear plane and the RMSE.

\begin{table}[H]
  \centering
\captionsetup{justification=centering}
  \hypertarget{Table 3}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Mean \% Error & RMSE & Mean \% Error & RMSE\\
    \hline
    ART policy & 0.64407\% &0.0027327 $c$  units & 0.201367\% & 0.0029924 $l$ units \\    
  GHLS policy & 0.62694\% & 0.0026704 $c$ units & 0.732262\% & 0.010799 $l$ units \\
  \hline
\end{tabular}
  \caption{Smoothness measures for labor policy functions ($c$ for model with capital and $n$ for model with capital). GHLS combined policy functions are reported.}
\end{table}

 \hyperlink{Table 3}{Table 3} reports the RMSE (root mean square error) and mean percent error from linear policy
functions. The mean percent error is calculated as $1/M\sum_{i=1}^N[\tilde{\textbf{n}}(i)-\hat{\textbf{n}}(i)]/\bar{n}$
where $N$ is the
number of periods, $\tilde{\textbf{n}}$ is the nonlinear approximation of the labor policy function, $\hat{\textbf{n}}$ is the linear regression model of $\tilde{\textbf{n}}$ fit to
the state variables, and $\bar{n}$ is steady state labor. The linear regression model $Y = XB$ is as follows:
\small
\begin{gather*}
  Y = \tilde{\textbf{n}},
  X = \begin{bmatrix}
    1 & g_t \\ 
    1 & s_t \\   
    1 & mp_t \\
    1 & in_t \\
    1 & c_t\\
    1 & k_t\\
    1 & x_t    
  \end{bmatrix},
  B = \begin{bmatrix}
    \beta_0 \\
    \beta_1
    \end{bmatrix}.
\end{gather*}
\normalsize

%The corresponding results for the model without
%capital is reported in \hyperlink{Appendix C}{Appendix C}.
